Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-29 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more writing in the edgb section

We start by presenting our result for EdGB gravity.
%
In Fig.~\ref{fig:edgb_exec_sum} we show the margelized posteriors of the coupling constant $\ell_{\rm GB}$,
for GW150914 (top panel) and GW200129 (middle panel), with and without the spin correction to the $(2,2,0)$
QNM.

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_cdf_varying_threshold.pdf}
\caption{(Color online).~The cumulative distribution function evaluated at the
cut-off $\Lambda_{\rm EFT}(\varepsilon, \gm)$ as a function of the parameter $\varepsilon$ for both
$\gm = m_2$ (solid and dashed lines) and $\gm = M_{f}$ (dot-dashed and dotted lines) without
(blue lines) and with (orange lines) linear-in-spin QNM corrections.
The horizontal lines lay at 0.68 and 0.90.
%
We see that the CDF curves for $\gm = M_{f}$ are above 90\% for $\varepsilon =
1/2$ for both events, with and without including the $j = 1$ dCS corrections to
the dominant QNM.
}
\label{fig:dcs_cdf}
\end{figure}

>>>>

We start by presenting our results for EdGB gravity.
%
In Fig.~\ref{fig:edgb_exec_sum} we show the margelized posteriors of the coupling constant $\ell_{\rm GB}$,
for GW150914 (top panel) and GW200129 (middle panel), with and without the spin correction to the $(2,2,0)$
QNM. The bottom panel panel shows the joint posterior combining both events.
%
We see for both events events the $N_{\rm max} = 0$ posteriors are characterized by a peak away from zero.
%
This does not mean that we are observing a deviantion from GR. We recall that the deviations from GR in the ParSpec framework
are controlled by $\gamma$, which here reads,
%
\begin{equation}
    \gamma_{\rm GB} = \left(\frac{c^2 \ell_{\rm GB}}{ G M_{\rm s}}\right)^4\,.
\end{equation}
%
As shown in Fig.~xxx, $\gamma_{\rm GB}$ does indeed have a posterior with maximum support near zero, indicating consistency
of our data with GR.
%
We also observe that the inclusion of the spin corrections (i.e., $N_{\rm max} = 1$) displaces the posteriors towards
smaller values of $\ell_{\rm GB}$.

As we stressed in Sec.~\ref{sec:remarks}, before we can draw any conclusions on
the allowed values for $\ell_{\rm GB}$ from our parameter estimation study, we
must first check whether the ``EFT''~\eqref{eq:eft_bound} and
``ParSpec''~\eqref{eq:parspec_bound} bounds are satisfied.
%
We do the former in Fig.~\ref{fig:edgb_cdf}.

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_cdf_varying_threshold.pdf}
\caption{(Color online).~The cumulative distribution function evaluated at the
cut-off $\Lambda_{\rm EFT}(\varepsilon, \gm)$ as a function of the parameter $\varepsilon$ for both
$\gm = m_2$ (solid and dashed lines) and $\gm = M_{f}$ (dot-dashed and dotted lines) without
(blue lines) and with (orange lines) linear-in-spin QNM corrections.
The horizontal lines lay at 0.68 and 0.90.
%
We see that the CDF curves for $\gm = M_{f}$ are above 90\% for $\varepsilon =
1/2$ for both events, with and without including the $n = 1$ dCS corrections to
the dominant QNM.
}
\label{fig:dcs_cdf}
\end{figure}
